---
title: Resume of Robert M. Romito
output: 
    word_document:
        reference_docx: resume-styles.docx
        df_print: "tibble"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(lubridate)
library(tibble)
```
###### rob@robertromito.com | https://linkedin.com/in/robertromito | https://github.com/robertromito

# Summary 

Software and computing are my career, hobby, and passion. I've been doing this for 25+ years and I still love it.
I enjoy learning, designing, architecting, prototyping, implementing, automating testing, automating deploying,
instrumenting, monitoring, bug hunting, performance tuning, and improving all the processes necessary to keep
systems running smoothly.

I'm comfortable working with other developers on detailed technical issues and with non-technical product owners
at a higher, value focused level. I prefer to be open and direct about the challenges and realities of building zero
downtime, distributed systems. I think it's very important for the non-technical side to have a feel for why our work
is so difficult to help them during discussions about timelines and budgets with their own Teams.

# Recent Experience [^1]

## American Red Cross

### Dirctor, Engineering | January 2020 - present

```{r}
first_day <- ymd("2015/03/30")
this_day <- today()
exp <- tribble(
~skill, ~start, ~end,
"AEM", first_day, this_day,
"Java", first_day, this_day,
"AWS", ymd("2015/05/04"), this_day,
)

```

### Enterprise Architect | January 2017 - January 2020

### Software Developer | March 2015 - January 2017

[^1]: Full professional history available on [LinkedIn](https://linkedin.com/in/robertromito)